---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fude

<!-- badges: start -->
[![R-CMD-check](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fude)](https://CRAN.R-project.org/package=fude)
<!-- badges: end -->

The fude package provides utilities to facilitate handling of Fude Polygon data downloadable from the Ministry of Agriculture, Forestry and Fisheries (MAFF) website. The word fude is a Japanese counter suffix used when referring to land parcels.

## Obtaining Data

Download the Fude Polygon data from the following release site of MAFF (only Japanese is available).

- <https://open.fude.maff.go.jp>

## Installation

You can install the released version of fude from CRAN with:
```r
install.packages("fude")
```

Or the development version from GitHub with:
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("takeshinishimura/fude")
```

## Usage

You can let R read the downloaded ZIP file without unzipping it.
```{r eval = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip")
```
```{r echo = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip", quiet = TRUE)
```

Those who wish to use a mouse or trackpad for file selection, which is especially common among R beginners, can do the following.

```{r eval = FALSE}
d <- read_fude(file.choose())
```

You can rename the local government codes to the Japanese municipality names for easier handling.

```{r}
d2 <- rename_fude(d)
```

It can also be renamed to romaji instead of Japanese.
```{r}
d3 <- d |> rename_fude(suffix = TRUE, romaji = "title", quiet = TRUE)
names(d3)
```

You can download the agricultural community boundary data corresponding to the Fude Polygon data from the MAFF website <https://www.maff.go.jp/j/tokei/census/shuraku_data/2020/ma/index.html>.
```{r eval = FALSE}
b <- get_boundary(d2)
```
```{r echo = FALSE, warning = FALSE}
b <- get_boundary(d2, quiet = TRUE)
```

You can draw a map combining Fude Polygons and agricultural community boundaries.
```{r eval = FALSE}
library(ggplot2)

db <- combine_fude(d2, b, city = "松山市", community = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")

ggplot() +
  geom_sf(data = db$fude, aes(fill = RCOM_NAME)) +
  geom_sf(data = db$boundary, fill = NA) +
  guides(fill = guide_legend(reverse = TRUE, title = "興居島の集落別耕地")) +
  theme_void()
```
```{r gogoshima, echo = FALSE, warning = FALSE, message = FALSE, dpi = 150}
library(ggplot2)

db <- combine_fude(d2, b, city = "松山市", community = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")

ggplot() +
  geom_sf(data = db$fude, aes(fill = RCOM_NAME)) +
  geom_sf(data = db$boundary, fill = NA) +
  guides(fill = guide_legend(reverse = TRUE, title = "興居島の集落別耕地")) +
  theme_void() +
  theme(text = element_text(family = "HiraKakuProN-W3"))
```

If you want to use `mapview()`, do the following.
```{r eval = FALSE}
library(mapview)

db <- combine_fude(d, b, city = "宇和島市", old_village = "遊子")
mapview::mapview(db$fude, zcol = "RCOM_NAME")
```
