---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fude

<!-- badges: start -->
[![R-CMD-check](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fude)](https://CRAN.R-project.org/package=fude)
<!-- badges: end -->

The fude package provides utilities to facilitate the handling of the Fude Polygon data downloadable from the Ministry of Agriculture, Forestry and Fisheries (MAFF) website. The word "fude" is a Japanese counter suffix used to denote land parcels.


## Obtaining Data

Download the Fude Polygon data from the following MAFF release site (available only in Japanese):

- <https://open.fude.maff.go.jp>

## Installation

You can install the released version of fude from CRAN with:
```r
install.packages("fude")
```

Or the development version from GitHub with:
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("takeshinishimura/fude")
```

## Usage

### Reading Fude Polygon Data

You can allow R to read the downloaded ZIP file directly without unzipping it.
```{r eval = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip")
```
```{r echo = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip", quiet = TRUE, supplementary = TRUE)
```

### Renaming the Local Government Code

Convert local government codes into Japanese municipality names for easier management.
```{r}
d2 <- rename_fude(d)
names(d2)
```

You can also rename the columns to Romaji instead of Japanese.
```{r}
d2 <- d |> rename_fude(suffix = TRUE, romaji = "title")
names(d2)
```

### Getting Agricultural Community Boundary Data

Download the agricultural community boundary data, which corresponds to the Fude Polygon data, from the MAFF website:
<https://www.maff.go.jp/j/tokei/census/shuraku_data/2020/ma/> (available only in Japanese).
```{r eval = FALSE}
b <- get_boundary(d)
```
```{r echo = FALSE, warning = FALSE}
b <- get_boundary(d, path = "~", quiet = TRUE)
```

You can easily create a map that combines Fude Polygons with agricultural community boundaries.
```{r gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
db <- combine_fude(d, b, city = "松山市", community = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")

library(ggplot2)

ggplot() +
  geom_sf(data = db$fude, aes(fill = RCOM_NAME), alpha = .8) +
  guides(fill = guide_legend(reverse = TRUE, title = "興居島の集落別耕地")) +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(text = element_text(family = "Hiragino Sans"))
```

**出典**：`r cite_fude(db)$ja`

### Data Assignment

- `db$fude`: Automatically assigns polygons on the boundaries to a community.
- `db$fude_split`: Provides cleaner boundaries, but polygon data near community borders may be divided.
```{r nosplit_gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150, fig.width = 12, fig.height = 8}
library(patchwork)

fude <- ggplot() +
  geom_sf(data = db$fude, aes(fill = RCOM_NAME), alpha = .8) +
  theme_void() +
  theme(legend.position = "none") +
  coord_sf(xlim = c(132.658, 132.678), ylim = c(33.887, 33.902))

fude_split <- ggplot() +
  geom_sf(data = db$fude_split, aes(fill = RCOM_NAME), alpha = .8) +
  theme_void() +
  theme(legend.position = "none") +
  coord_sf(xlim = c(132.658, 132.678), ylim = c(33.887, 33.902))

fude + fude_split
```

If you need to adjust this automatic assignment, you will need to write custom code.
The rows that require attention can be identified with the following command.
```{r message = FALSE}
# head(sf::st_drop_geometry(db$fude[db$fude$polygon_uuid %in% db$fude_split$polygon_uuid[duplicated(db$fude_split$polygon_uuid)], c("polygon_uuid", "PREF_NAME", "CITY_NAME", "KCITY_NAME", "RCOM_NAME", "RCOM_KANA", "RCOM_ROMAJI")]))
library(dplyr)
library(sf)

db$fude |>
  filter(polygon_uuid %in% (db$fude_split |> filter(duplicated(polygon_uuid)) |> pull(polygon_uuid))) |>
  st_drop_geometry() |>
  select(polygon_uuid, KCITY_NAME, RCOM_NAME, RCOM_KANA, RCOM_ROMAJI) |>
  head()
```

### Review Fude Polygon Data

You can review Fude Polygon data in detail.
```{r shiny_fude, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(shiny)

s <- shiny_fude(db, community = TRUE)
# shiny::shinyApp(ui = s$ui, server = s$server)
```

This feature was heavily inspired by the following website: <https://brendenmsmith.com/blog/shiny_map_filter/>.

### Using `mapview` package

If you want to use `mapview()`, do the following.
```{r eval = FALSE}
db1 <- combine_fude(d, b, city = "伊方町")
db2 <- combine_fude(d, b, city = "八幡浜市")
db3 <- combine_fude(d, b, city = "西予市", kcity = "三瓶|二木生|三島|双岩")

db <- bind_fude(db1, db2, db3)

library(mapview)

mapview::mapview(db$fude, zcol = "RCOM_NAME", layer.name = "農業集落名")
```
