---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fude

<!-- badges: start -->
[![R-CMD-check](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fude)](https://CRAN.R-project.org/package=fude)
<!-- badges: end -->

The fude package provides utilities to facilitate the handling of the Fude Polygon data downloadable from the Ministry of Agriculture, Forestry and Fisheries (MAFF) website. The word "fude" is a Japanese counter suffix used to denote land parcels.


## Obtaining Data

Download the Fude Polygon data from the following MAFF release site (available only in Japanese):

- <https://open.fude.maff.go.jp>

## Installation

You can install the released version of fude from CRAN with:
```r
install.packages("fude")
```

Or the development version from GitHub with:
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("takeshinishimura/fude")
```

## Usage

### Reading Fude Polygon Data

You can let R read the downloaded ZIP file directly without unzipping it.
```{r eval = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip")
```
```{r echo = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip", quiet = TRUE, supplementary = TRUE)
```

### Renaming Columns

You can convert local government codes into Japanese municipality names for easier management.
```{r}
d2 <- rename_fude(d)
names(d2)
```

You can also rename the columns to Romaji instead of Japanese.
```{r}
d2 <- d |> rename_fude(suffix = TRUE, romaji = "title")
names(d2)
```

### Getting Agricultural Community Boundary Data

You can download the agricultural community boundary data, which corresponds to the Fude Polygon data, from the MAFF website at   <https://www.maff.go.jp/j/tokei/census/shuraku_data/2020/ma/> (available only in Japanese).
```{r eval = FALSE}
b <- get_boundary(d)
```
```{r echo = FALSE, warning = FALSE}
b <- get_boundary(d, path = "~", quiet = TRUE)
```

You can easily create a map that combines Fude Polygons with agricultural community boundaries.
```{r gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
db <- combine_fude(d, b, city = "松山市", community = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")

library(ggplot2)

ggplot() +
  geom_sf(data = db$fude_split, aes(fill = RCOM_NAME)) +
  guides(fill = guide_legend(reverse = TRUE, title = "興居島の集落別耕地")) +
  theme_void() +
  theme(text = element_text(family = "Hiragino Sans"))
```

**出典**：`r cite_fude(db)$ja`

Polygon data near community borders may be divided.
To avoid this, use `db$fude`.
```{r nosplit_gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(ggforce)

ggplot() +
  geom_sf(data = db$community, fill = NA) +
  geom_sf(data = db$fude, aes(fill = RCOM_ROMAJI)) +
  geom_mark_hull(data = db$fude, 
                 aes(x = point_lng, y = point_lat,
                     fill = RCOM_ROMAJI,
                     label = RCOM_ROMAJI),
                 colour = NA,
                 expand = unit(1, "mm"),
                 radius = unit(1, "mm"),
                 label.fontsize = 9,
                 label.family = "Helvetica",
                 label.fill = NA,
                 label.colour = "black",
                 label.buffer = unit(1, "mm"),
                 con.colour = "gray70") +
  theme_void() +
  theme(legend.position = "none")
```

**Source**: `r cite_fude(db)$en`

Polygons on community boundaries are not divided but are assigned to one of the communities.
If you need to adjust this automatic assignment, you will need to write custom code.
The rows that require attention can be identified with the following command.
```{r message = FALSE}
library(dplyr)
library(sf)

# head(sf::st_drop_geometry(db$fude[db$fude$polygon_uuid %in% db$fude_split$polygon_uuid[duplicated(db$fude_split$polygon_uuid)], c("polygon_uuid", "PREF_NAME", "CITY_NAME", "KCITY_NAME", "RCOM_NAME", "RCOM_KANA", "RCOM_ROMAJI")]))
db$fude |>
  filter(polygon_uuid %in% (db$fude_split |> filter(duplicated(polygon_uuid)) |> pull(polygon_uuid))) |>
  sf::st_drop_geometry() |>
  select(polygon_uuid, KCITY_NAME, RCOM_NAME, RCOM_KANA, RCOM_ROMAJI) |>
  head()
```

### Visualizing Fude Polygon Data

You can confirm Fude Polygon data in detail.
```{r shiny_fude, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(shiny)

s <- shiny_fude(db, community = TRUE)
# shiny::shinyApp(ui = s$ui, server = s$server)
```

This feature was heavily inspired by the following website: <https://brendenmsmith.com/blog/shiny_map_filter/>.

### Using `mapview` package

If you want to use `mapview()`, do the following.
```{r eval = FALSE}
db1 <- combine_fude(d, b, city = "伊方町")
db2 <- combine_fude(d, b, city = "八幡浜市")
db3 <- combine_fude(d, b, city = "西予市", old_village = "三瓶|二木生|三島|双岩")
db <- bind_fude(db1, db2, db3)

library(mapview)

mapview::mapview(db$fude, zcol = "RCOM_NAME", layer.name = "農業集落名")
```
