---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fude

<!-- badges: start -->
[![R-CMD-check](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fude)](https://CRAN.R-project.org/package=fude)
<!-- badges: end -->

The fude package provides utilities to facilitate the handling of the Fude Polygon data downloadable from the Ministry of Agriculture, Forestry and Fisheries (MAFF) website. The word "fude" is a Japanese counter suffix used to denote land parcels.

## Obtain data
Fude Polygon data can now be downloaded from two different MAFF websites (both available only in Japanese):

1. **GeoJSON format**:  
   <https://open.fude.maff.go.jp>

2. **FlatGeobuf format**:  
   <https://www.maff.go.jp/j/tokei/census/shuraku_data/2020/mb/>

## Install the package

You can install the released version of fude from CRAN with:
```r
install.packages("fude")
```

Or the development version from GitHub with:
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("takeshinishimura/fude")
```

## Usage

### Read Fude Polygon data

There are two ways to load Fude Polygon data, depending on how the data was obtained:

1. **From a locally saved ZIP file**:  
This method works for both GeoJSON (from Obtaining Data #1) and FlatGeobuf (from Obtaining Data #2) formats. You can load a ZIP file saved on your computer without unzipping it.
```{r eval = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip")
```
```{r echo = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip", quiet = TRUE, supplementary = TRUE)
```

2. **By specifying a prefecture name or code**:  
This method is available only for FlatGeobuf data (from Obtaining Data #2). Provide the name of a prefecture (e.g., "愛媛") or its corresponding prefecture code (e.g., "38"), and the required FlatGeobuf format ZIP file will be automatically downloaded and loaded.
```{r eval = FALSE}
d2 <- read_fude(pref = "愛媛")
```
```{r echo = FALSE}
d2 <- read_fude("~/MB0001_2025_2020_38.zip", quiet = TRUE)
```

### List the contents of Fude Polygon datal

```{r}
ls_fude(d)
```

### Rename the local government code

**Note:** This feature is available only for data obtained from GeoJSON (Obtaining Data #1).

Convert local government codes into Japanese municipality names for easier management.
```{r}
dro <- rename_fude(d)
names(dro)
```

You can also rename the columns to Romaji instead of Japanese.
```{r}
dro <- d |>
  rename_fude(suffix = TRUE, romaji = "title", quiet = FALSE)
```

### Get agricultural community boundary data

Download the agricultural community boundary data, which corresponds to the Fude Polygon data, from the MAFF website:
<https://www.maff.go.jp/j/tokei/census/shuraku_data/2020/ma/> (available only in Japanese).
```{r eval = FALSE}
b <- get_boundary(d)
```
```{r echo = FALSE, warning = FALSE}
b <- get_boundary(d, path = "~", quiet = TRUE)
```

### Combine Fude Polygons with agricultural community boundaries

You can easily combine Fude Polygons with agricultural community boundaries to create enriched spatial analyses or maps.

```{r gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(ggplot2)

db <- combine_fude(d2, b, city = "松山市", rcom = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")

ggplot() +
  geom_sf(data = db$fude, aes(fill = rcom_name), alpha = .8) +
  guides(fill = guide_legend(reverse = TRUE, title = "興居島の集落別耕地")) +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(text = element_text(family = "Hiragino Sans"))
```

**出典**：`r cite_fude(db)$ja`

Data enables extraction based on municipality names, former municipality names, and agricultural community names.

**Note:** This feature is available only for data obtained from FlatGeobuf (Obtaining Data #2).

```{r message = FALSE}
extract_fude(d2, city = "松山市", kcity = "興居島")
```

### Explore Fude Polygon data

You can explore Fude Polygon data interactively.
```{r warning = FALSE, message = FALSE}
library(shiny)

s <- shiny_fude(db, rcom = TRUE)
# shinyApp(ui = s$ui, server = s$server)
```

### Read data from the MAFF database

You can read data from the MAFF database ([地域の農業を見て・知って・活かすDB](https://www.maff.go.jp/j/tokei/census/shuraku_data/)).
```{r ikasu, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(dplyr)

b1 <- get_boundary(d2, path = "~", boundary_type = 1, quiet = TRUE)
b2 <- get_boundary(d2, path = "~", boundary_type = 2, quiet = TRUE)
b3 <- get_boundary(d2, path = "~", boundary_type = 3, quiet = TRUE)

m1 <- b1 |>
  read_ikasudb("~/IA0001_2023_2020_38.xlsx") |>
  mutate(
    地域類型1次分類 = factor(
      地域類型1次分類,
      levels = 1:4,
      labels = c("都市的地域", "平地農業地域", "中間農業地域", "山間農業地域")
    )
  )

ggplot() +
  geom_sf(data = m1, aes(fill = 地域類型1次分類)) +
  scale_fill_brewer(palette = "BuGn", na.translate = FALSE) +
  theme_void() +
  theme(text = element_text(family = "Hiragino Sans"))
```

**資料**：`r cite_fude(m1)$ja`

### Use the `mapview` package

If you want to use `mapview()`, do the following.
```{r eval = FALSE}
db1 <- combine_fude(d, b, city = "伊方町")
db2 <- combine_fude(d, b, city = "八幡浜市")
db3 <- combine_fude(d, b, city = "西予市", kcity = "三瓶|二木生|三島|双岩")

db <- bind_fude(db1, db2, db3)
db$fude <- sf::st_transform(db$fude, crs = 3857)

library(mapview)

mapview(db$fude, zcol = "rcom_name", layer.name = "農業集落名")
```
