---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fude

<!-- badges: start -->
[![R-CMD-check](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fude)](https://CRAN.R-project.org/package=fude)
<!-- badges: end -->

The fude package provides utilities to facilitate the handling of the Fude Polygon data downloadable from the Ministry of Agriculture, Forestry and Fisheries (MAFF) website. The word "fude" is a Japanese counter suffix used to denote land parcels.


## Obtaining Data

Download the Fude Polygon data from the following MAFF release site (available only in Japanese):

- <https://open.fude.maff.go.jp>

## Installation

You can install the released version of fude from CRAN with:
```r
install.packages("fude")
```

Or the development version from GitHub with:
```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("takeshinishimura/fude")
```

## Usage

You can allow R to read the downloaded ZIP file directly without unzipping it.
```{r eval = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip")
```
```{r echo = FALSE}
library(fude)
d <- read_fude("~/2022_38.zip", quiet = TRUE, supplementary = TRUE)
```

You can convert the local government codes into Japanese municipality names for more convenient management.
```{r}
d2 <- rename_fude(d)
names(d2)
```

It can also be renamed to romaji instead of Japanese.
```{r}
d2 <- d |> rename_fude(suffix = TRUE, romaji = "title")
names(d2)
```

You can download the agricultural community boundary data, which corresponds to the Fude Polygon data, from the MAFF website at  <https://www.maff.go.jp/j/tokei/census/shuraku_data/2020/ma/> (available only in Japanese).
```{r eval = FALSE}
b <- get_boundary(d)
```
```{r echo = FALSE, warning = FALSE}
b <- get_boundary(d, path = "~", quiet = TRUE)
```

You can effortlessly create a map that integrates Fude Polygons with agricultural community boundaries.
```{r gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
db <- combine_fude(d, b, city = "松山市", community = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")

library(ggplot2)

ggplot() +
  geom_sf(data = db$fude_split, aes(fill = RCOM_NAME)) +
  guides(fill = guide_legend(reverse = TRUE, title = "興居島の集落別耕地")) +
  theme_void() +
  theme(text = element_text(family = "Hiragino Sans"))
```

**出典**：`r cite_fude(db)$ja`

Polygon data close to community borders may be divided.
To avoid this, utilize `db$fude`.
```{r nosplit_gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(ggforce)

ggplot() +
  geom_sf(data = db$community, fill = NA) +
  geom_sf(data = db$fude, aes(fill = RCOM_ROMAJI)) +
  geom_mark_hull(data = db$fude, 
                 aes(x = point_lng, y = point_lat,
                     fill = RCOM_ROMAJI,
                     label = RCOM_ROMAJI),
                 colour = NA,
                 expand = unit(1, "mm"),
                 radius = unit(1, "mm"),
                 label.fontsize = 9,
                 label.family = "Helvetica",
                 label.fill = NA,
                 label.colour = "black",
                 label.buffer = unit(1, "mm"),
                 con.colour = "gray70") +
  theme_no_axes() +
  theme(legend.position = "none")
```

**Source**: `r cite_fude(db)$en`

Polygons situated on community boundaries are not divided but are allocated to one of the communities.
Should there be a need to adjust this automatic assignment, custom coding will be necessary.
The rows that require consideration can be extracted with the following command.
```{r message = FALSE}
library(dplyr)
library(sf)

# head(sf::st_drop_geometry(db$fude[db$fude$polygon_uuid %in% db$fude_split$polygon_uuid[duplicated(db$fude_split$polygon_uuid)], c("polygon_uuid", "PREF_NAME", "CITY_NAME", "KCITY_NAME", "RCOM_NAME", "RCOM_KANA", "RCOM_ROMAJI")]))
db$fude |>
  filter(polygon_uuid %in% (db$fude_split |> filter(duplicated(polygon_uuid)) |> pull(polygon_uuid))) |>
  select(polygon_uuid, PREF_NAME, CITY_NAME, KCITY_NAME, RCOM_NAME, RCOM_KANA, RCOM_ROMAJI) |>
  sf::st_drop_geometry() |>
  head()
```

The gghighlight package enables practical and effective visualization.
```{r facet_wrap_gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(forcats)
library(gghighlight)

db$community <- db$community %>%
  mutate(across(c(RCOM_NAME, RCOM_KANA, RCOM_ROMAJI), forcats::fct_rev))
db$fude <- db$fude %>%
  mutate(across(c(RCOM_NAME, RCOM_KANA, RCOM_ROMAJI), forcats::fct_rev))

ggplot() +
  geom_sf(data = db$community, aes(fill = RCOM_NAME), alpha = 0) +
  geom_sf(data = db$fude, aes(fill = RCOM_NAME), linewidth = 0) +
  gghighlight() +
  facet_wrap(vars(RCOM_NAME)) +
  theme_void() +
  theme(legend.position = "none",
        text = element_text(family = "Hiragino Sans"))
```

**出典**：`r cite_fude(db)$ja`

```{r facet_wrap_gogoshima_hist, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
ggplot(data = db$fude, aes(x = as.numeric(a), fill = land_type_jp)) +
  geom_histogram(position = "identity", alpha = .5) +
  labs(x = "面積（a）",
       y = "頻度") +
  facet_wrap(vars(RCOM_NAME)) +
  labs(fill = "耕地の種類") +
  theme_minimal() +
  theme(text = element_text(family = "Hiragino Sans"))
```

There are `r length(names(db))` types of objects obtained by `combine_fude()`, as follows:
```{r}
names(db)
```

If you want to be particular about the details of the map, for example, execute the following code.
```{r gogoshima_with_minimap, eval = FALSE, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
db <- combine_fude(d, b, city = "松山市", old_village = "興居島", community = "^(?!釣島).*")

library(ggrepel)
library(cowplot)

minimap <- ggplot() +
  geom_sf(data = db$lg, aes(fill = fill)) +
  geom_sf_text(data = db$lg, aes(label = city_kanji), family = "Hiragino Sans") +
  gghighlight(fill == 1) +
  geom_sf(data = db$community_union, fill = "black", linewidth = 0) +
  theme_void() +
  theme(panel.background = element_rect(fill = "aliceblue")) +
  scale_fill_manual(values = c("white", "gray"))

mainmap <- ggplot() +
  geom_sf(data = db$community, fill = "white") +
  geom_sf(data = db$fude, aes(fill = RCOM_NAME)) +
  geom_point(data = db$community, aes(x = x, y = y), colour = "gray") +
  geom_text_repel(data = db$community,
                  aes(x = x, y = y, label = RCOM_NAME),
                  nudge_x = c(-.01, .01, -.01, -.012, .005, -.01, .01, .01),
                  nudge_y = c(.005, .005, 0, .01, -.005, .01, 0, -.005),
                  min.segment.length = .01,
                  segment.color = "gray",
                  size = 3,
                  family = "Hiragino Sans") +
  theme_void() +
  theme(legend.position = "none")

ggdraw(mainmap) +
  draw_plot(
    {minimap +
       geom_rect(aes(xmin = 132.47, xmax = 133.0,
                     ymin = 33.72, ymax = 34.05),
                 fill = NA,
                 colour = "black",
                 size = .5) +
       coord_sf(xlim = c(132.47, 133.0),
                ylim = c(33.72, 34.05),
                expand = FALSE) +
       theme(legend.position = "none")
    },
    x = .7, 
    y = 0,
    width = .3, 
    height = .3)
```

If you want to use `mapview()`, do the following.
```{r eval = FALSE}
db1 <- combine_fude(d, b, city = "伊方町")
db2 <- combine_fude(d, b, city = "八幡浜市")
db3 <- combine_fude(d, b, city = "西予市", old_village = "三瓶|二木生|三島|双岩")
db <- bind_fude(db1, db2, db3)

library(mapview)

mapview::mapview(db$fude, zcol = "RCOM_NAME", layer.name = "農業集落名")
```

The possible values for `community` in `combine_fude()` can be listed as follows.
```{r matsuyama, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(data.tree)

b[[1]] |>
  filter(grepl("松山", KCITY_NAME)) |>
  mutate(pathString = paste(PREF_NAME, CITY_NAME, KCITY_NAME, RCOM_NAME, sep = "/")) |>
  data.tree::as.Node() |>
  print(limit = 10)
ggplot(data = b[[1]] |> filter(grepl("松山", KCITY_NAME))) + 
  geom_sf(fill = NA) +
  geom_sf_text(aes(label = RCOM_NAME), size = 2, family = "Hiragino Sans") +
  theme_void()
```

`shiny_fude()`

```{r shiny_fude, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(shiny)

s <- shiny_fude(db$fude)
# shiny::shinyApp(ui = s$ui, server = s$server)
```

You can also visualize the relationship between the residences of farmers and their farmland.
```{r farmer1, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
db <- combine_fude(d, b, city = "松山", community = "和気|安城寺|長戸|久万ノ台")

set.seed(200)
probabilities <- c(0.97, 0.01, 0.005, 0.005, 0.005, 0.005)
names(probabilities) <- LETTERS[1:length(probabilities)]
db$fude$farmer = factor(sample(names(probabilities),
                               nrow(db$fude),
                               replace = TRUE,
                               prob = probabilities))

farm <- db$fude |>
  group_by(farmer) |>
  summarise(geometry = sf::st_union(geometry) |> sf::st_centroid()) |>
  sf::st_set_crs(4326)

farm_radius <- farm |>
  sf::st_transform(crs = sp::CRS("+init=epsg:32632")) |>
  sf::st_buffer(dist = units::as_units(1, "km")) |>
  sf::st_transform(crs = 4326)

library(osmdata)
library(ggmapinset)
library(ggrepel)

bbox <- sf::st_bbox(db$fude)

streets <- bbox |>
  osmdata::opq() |>
  osmdata::add_osm_feature(key = "highway", 
                           value = c("motorway", "primary", "secondary", "tertiary",
                                     "residential", "living_street",
                                     "unclassified", "service", "footway")) |>
  osmdata::osmdata_sf()

river <- bbox |>
  osmdata::opq() |>
  osmdata::add_osm_feature(key = "waterway", value = "river") |>
  osmdata::osmdata_sf()

inset1 <- configure_inset(
    centre = sf::st_geometry(farm)[farm$farmer == "F"],
    scale = 3,
    translation = c(-4, 1),
    radius = 1, units = "km"
  )
inset2 <- configure_inset(
    centre = sf::st_geometry(farm)[farm$farmer == "E"],
    scale = 3,
    translation = c(4, -3),
    radius = 1, units = "km"
  )

farm$x <- sf::st_coordinates(farm)[, 1]
farm$y <- sf::st_coordinates(farm)[, 2]

ggplot(data = db$fude) +
  geom_sf(data = streets$osm_lines, colour = "gray") +
  geom_sf(data = river$osm_lines, colour = "skyblue") +
  geom_sf(aes(fill = farmer, colour = farmer), alpha = .5) +
  geom_sf(data = farm, aes(colour = farmer)) +
  geom_text_repel(data = farm,
                  aes(x = x, y = y, label = farmer),
                  nudge_x = c(.02, .02, .02, -.01, .02, -.012),
                  nudge_y = c(.01, 0, -.005, -.005, .01, -.005),
                  min.segment.length = 0,
                  segment.color = "black",
                  size = 3,
                  family = "Helvetica") +
  geom_sf_inset(data = streets$osm_lines, colour = "gray", map_base = "none", inset = inset1) +
  geom_sf_inset(data = river$osm_lines, colour = "skyblue", map_base = "none", inset = inset1) +
  geom_sf_inset(aes(fill = farmer, colour = farmer), alpha = .5, map_base = "none", inset = inset1) +
  geom_inset_frame(inset = inset1) +
  geom_sf_inset(data = streets$osm_lines, colour = "gray", map_base = "none", inset = inset2) +
  geom_sf_inset(data = river$osm_lines, colour = "skyblue", map_base = "none", inset = inset2) +
  geom_sf_inset(aes(fill = farmer, colour = farmer), alpha = .5, map_base = "none", inset = inset2) +
  geom_inset_frame(inset = inset2) +
  theme_void() +
  theme(legend.position = "none")
```

**出典**：`r cite_fude(db)$ja`
