---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fude

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/fude)](https://CRAN.R-project.org/package=fude)
<!-- badges: end -->

The fude package provides utilities to facilitate handling of Fude Polygon data downloadable from the Ministry of Agriculture, Forestry and Fisheries (MAFF) website. The word "fude" ("筆") is a Japanese counter suffix used when referring to land parcels.

## Get Data

Download the Fude Polygon data from the following release site of MAFF.

* <https://open.fude.maff.go.jp> (Only Japanese is available.)

## Installation

You can install the released version of fude from CRAN:

``` r
install.packages("fude")
```

Or the development version from GitHub:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("takeshinishimura/fude")
```

## Example

You can let R read the downloaded ZIP file without unzipping it.
This function was inspired by [kokudosuuchi: Utilities for 'Kokudo Suuchi'](https://CRAN.R-project.org/package=kokudosuuchi).

```{r example}
library(fude)

d <- read_fude("~/2022_382019.zip")
```

You can change the local government code to the Japanese municipality name for easier handling.

```{r example2}
d <- rename_fude(d)
```
