---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fude

<!-- badges: start -->
[![R-CMD-check](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml/badge.svg)](https://github.com/takeshinishimura/fude/actions/workflows/check-standard.yaml)
[![CRAN status](https://www.r-pkg.org/badges/version/fude)](https://CRAN.R-project.org/package=fude)
<!-- badges: end -->

The fude package provides utilities to facilitate handling of Fude Polygon data downloadable from the Ministry of Agriculture, Forestry and Fisheries (MAFF) website. The word fude is a Japanese counter suffix used when referring to land parcels.

## Obtaining Data

Download the Fude Polygon data from the following release site of MAFF (only Japanese is available).

- <https://open.fude.maff.go.jp>

## Installation

You can install the released version of fude from CRAN with:

``` r
install.packages("fude")
```

Or the development version from GitHub with:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("takeshinishimura/fude")
```

## Usage

You can let R read the downloaded ZIP file without unzipping it.
This function was inspired by [kokudosuuchi: Utilities for 'Kokudo Suuchi'](https://CRAN.R-project.org/package=kokudosuuchi).

```{r usage}
library(fude)
d <- read_fude("~/2022_382019.zip")
```

Those who wish to use a mouse or trackpad for file selection, which is especially common among R beginners, can do the following.

```{r eval = FALSE}
d <- read_fude(file.choose())
```

You can rename the local government codes to the Japanese municipality names for easier handling.

```{r}
d2 <- rename_fude(d)
```

It can also be renamed to romaji instead of Japanese.

```{r}
d3 <- d |> rename_fude(suffix = FALSE, romaji = "title")
```
