---
title: "Structure of combined Fude Polygon data with agricultural community boundary data"

output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Structure of combined Fude Polygon data with agricultural community boundary data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Structure of combined Fude Polygon data with agricultural community boundary data

```{r echo = TRUE, warning = FALSE, message = FALSE}
library(fude)

d <- read_fude("~/2022_38.zip", quiet = TRUE, supplementary = TRUE)
b <- get_boundary(d, path = "~", quiet = TRUE)

d2 <- read_fude("~/MB0001_2025_2020_38.zip", quiet = TRUE)
```

## GeoJSON data characteristics (obtain data #1)

```{r echo = TRUE, warning = FALSE, message = FALSE}
library(sf)

db <- d |>
  lapply(st_transform, crs = 4612) |>
  combine_fude(b, city = "松山市", rcom = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")
```

There are `r length(names(db))` types of objects obtained by `combine_fude()`, as follows:
```{r}
names(db)
```

```{r gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(ggplot2)

ggplot() +
  geom_sf(data = db$fude, aes(fill = rcom_romaji), alpha = .8) +
  guides(fill = guide_legend(reverse = TRUE, title = "Agricultural community")) +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(text = element_text(family = "Hiragino Sans"))
```

**Source**: `r cite_fude(db)$en`

### Data assignment

- `db$fude`: Automatically assigns polygons on the boundaries to a community.
- `db$fude_split`: Provides cleaner boundaries, but polygon data near community borders may be divided.
```{r nosplit_gogoshima, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150, fig.width = 6, fig.height = 4}
library(patchwork)

fude <- ggplot() +
  geom_sf(data = db$fude, aes(fill = rcom_romaji), alpha = .8) +
  theme_void() +
  theme(legend.position = "none") +
  coord_sf(xlim = c(132.658, 132.678), ylim = c(33.887, 33.902))

fude_split <- ggplot() +
  geom_sf(data = db$fude_split, aes(fill = rcom_romaji), alpha = .8) +
  theme_void() +
  theme(legend.position = "none") +
  coord_sf(xlim = c(132.658, 132.678), ylim = c(33.887, 33.902))

fude + fude_split
```

**Source**: `r cite_fude(db)$en`

If you need to adjust this automatic assignment, you will need to write custom code.
The rows that require attention can be identified with the following command.
```{r message = FALSE}
library(dplyr)

db$fude |>
  filter(polygon_uuid %in% (db$fude_split |> filter(duplicated(polygon_uuid)) |> pull(polygon_uuid))) |>
  st_drop_geometry() |>
  select(polygon_uuid, kcity_name, rcom_name, rcom_romaji) |>
  head()
```

## FlatGeobuf data characteristics (obtain data #2)

The FlatGeobuf format offers a more efficient alternative to GeoJSON.
A notable feature of this format is that each record already includes an **accurately assigned agricultural community code**.
```{r gogoshimafgb, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
db <- combine_fude(d2, b, city = "松山市", rcom = "由良|北浦|鷲ケ巣|門田|馬磯|泊|御手洗|船越")

ggplot() +
  geom_sf(data = db$fude, aes(fill = rcom_romaji), alpha = .8) +
  guides(fill = guide_legend(reverse = TRUE, title = "Agricultural community")) +
  theme_void() +
  theme(legend.position = "bottom") +
  theme(text = element_text(family = "Hiragino Sans"))
```

**Source**: `r cite_fude(db)$en`

# Possible values for `rcom` in `combine_fude()` and `extract_boundary()`

```{r rcom_in_data, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(data.tree)

tree <- b[[1]] |>
  filter(grepl("松山", kcity_name)) |>
  mutate(pathString = paste(pref_name, city_name, kcity_name, rcom_name, sep = "/")) |>
  data.tree::as.Node()

tree$Do(\(x) {x$n <- if (x$isLeaf) NA_integer_ else x$count})
data.tree::SetFormat(tree, "n", \(x) if (is.na(x)) "-" else x)
print(tree, "n", limit = 30)

ggplot(data = b[[1]] |> filter(grepl("松山", kcity_name))) + 
  geom_sf(fill = NA) +
  geom_sf_text(aes(label = rcom_name), size = 2, family = "Hiragino Sans") +
  theme_void()
```

**出典**：`r cite_fude(b)$ja`

```{r rcom_in_data_tree, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(collapsibleTree)

b[[1]] |>
  filter(grepl("松山", city_name)) |>
  distinct(pref_name, city_name, kcity_name, rcom_name) |>
  (\(x) collapsibleTree(
    x,
    hierarchy = names(x),
    root = "・"
  ))()
```

# Possible values for `kcity` in `combine_fude()` and `extract_boundary()`

```{r kcity_in_data, echo = TRUE, warning = FALSE, message = FALSE, dpi = 150}
library(paletteer)

ggplot(b[[1]] |> filter(city_name == "松山市")) +
  geom_sf(aes(fill = kcity_name), alpha = .8) +
  theme_void() +
  theme(text = element_text(family = "Hiragino Sans")) +
  paletteer::scale_fill_paletteer_d("Polychrome::kelly")
```

**出典**：`r cite_fude(b)$ja`
